CDSR Human Data/Modelling Paper

### 2013-09-12 scenarios/cdsr/trunk/papers/ACS2013/main.tex
jk flipped table 3

\begin{table}
\centerline{
\begin{tabular}{l c c c }
\hline
Domain & \multicolumn{3}{c}{Map/Bottleneck} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} \\
Stim ID & P1 & P2 & P3 \\
(g) & $1.1707$ & $\mathbf{4.6667}$ \\ % 1_1
(h) & $1.1707$ & $\mathbf{4.7561}$ \\ % 1_2
\\
\hline
Domain & \multicolumn{3}{c}{Classrom/Front of Room} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} \\
Stim ID & P1 & P2 & P3 \\
(a) & $\mathbf{3.5122}$ & $2.6341$ & $1.9024$ \\ % 2_1
(c) & $\mathbf{4.7073}$ & $2.9024$ & $1.3571$ \\ % 2_6
(c-flipped) & $1.244$ & $2.9268$ & $\mathbf{4.6429}$ \\ %2_7
(e) & $\mathbf{4.7561}$ & $2.0000$ & $1.2439$ \\ %2_2
(e-flipped) & $1.2439$ & $1.8500$ & $\mathbf{4.7073}$ \\ % 2_3
(f) & $\mathbf{4.8292}$ & $2.0976$ & $1.2750$ \\ % 2_4
(f-flipped) & $1.1463$ & $2.3171$ & $\mathbf{4.6585}$ \\ % 2_5
\\
\hline
Domain & \multicolumn{3}{c}{Military Engagement/Safe Region} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} \\
Stim ID & P1 & P2 & P3\\
(i) & $1.1951$ & $4.3902$ & $\mathbf{4.9024}$ \\ % 3_1
(j) & $1.0952$ & $2.2927$ & $\mathbf{4.5122}$ \\ % 3_2
(k) & $1.0714$ & $2.7804$ & $\mathbf{4.6585}$ \\ % 3_3
(l) & $1.2327$ & $3.1667$ & $\mathbf{4.7073}$\\ % 3_4
\\
\hline
\hline
\end{tabular}
}
\label{tab:point-likert-scores}
\caption{Average Likert Ratings per Point by Domain.}
\end{table}

>>>>

\begin{table}
\centerline{
\begin{tabular}{l c c c c c c c }
\hline
\hline
%Domain & \multicolumn{7}{l}{Map/Bottleneck} \\
\textbf{Map} & g & h & ~ & ~ & ~ & ~ & ~ \\ 
P1 & $1.1707$ & $1.1707$ & ~ & ~ & ~ & ~ & ~ \\
P2 & $\mathbf{4.6667}$ & $\mathbf{4.7561}$ & ~ & ~ & ~ & ~ & ~ \\
P3 & $1.85$ & $1.585$ & ~ & ~ & ~ & ~ & ~ \\
\hline
%Domain & \multicolumn{7}{l}{Classrom/Front of Room} \\
\textbf{Classroom}& a & c & c-flipped & e & e-flipped & f & f-flipped \\
P1 & $\mathbf{3.5122}$ & $\mathbf{4.7073}$ & $1.244$  & $\mathbf{4.7561}$ & $1.2439$ & $\mathbf{4.8292}$ & $1.1463$\\
P2 & $2.6341$ & $2.9024$ & $2.9268$ & $2.0000$ & $1.8500$ & $2.0976$ & $2.3171$\\
P3 & $1.9024$ & $1.3571$ & $\mathbf{4.6429}$ & $1.2439$ & $\mathbf{4.7073}$ & $1.2750$ & $\mathbf{4.6585}$\\
\hline
%Domain & \multicolumn{7}{l}{Military Engagement/Safe Region} \\
\textbf{Military} & i & j & k & l & ~ & ~ & ~ \\
P1 & $1.1951$ & $1.0952$ & $1.0714$ & $1.2327$ & ~ & ~ & ~ \\
P2 & $4.3902$ & $2.2927$ & $2.7804$ & $3.1667$& ~ & ~ & ~ \\
P3 & $\mathbf{4.9024}$ & $\mathbf{4.5122}$ & $\mathbf{4.6585}$ & $\mathbf{4.7073}$ & ~ & ~ & ~ \\
\hline
\end{tabular}
}
\label{tab:point-likert-scores}
\caption{Average Likert Ratings per Point by Domain and stimulus.}
\end{table}

%\begin{table}
%\centerline{
%\begin{tabular}{l c c c }
%\hline
%\hline
%Domain & \multicolumn{3}{c}{Map/Bottleneck} \\
%% ~ & \multicolumn{3}{c}{Average Likert Rating} \\
%Stim ID & P1 & P2 & P3 \\
%(g) & $1.1707$ & $\mathbf{4.6667}$ & $1.85$\\ % 1_1
%(h) & $1.1707$ & $\mathbf{4.7561}$ & $1.585$ \\ % 1_2
%\\
%\hline
%Domain & \multicolumn{3}{c}{Classrom/Front of Room} \\
%% ~ & \multicolumn{3}{c}{Average Likert Rating} \\
%Stim ID & P1 & P2 & P3 \\
%(a) & $\mathbf{3.5122}$ & $2.6341$ & $1.9024$ \\ % 2_1
%(c) & $\mathbf{4.7073}$ & $2.9024$ & $1.3571$ \\ % 2_6
%(c-flipped) & $1.244$ & $2.9268$ & $\mathbf{4.6429}$ \\ %2_7
%(e) & $\mathbf{4.7561}$ & $2.0000$ & $1.2439$ \\ %2_2
%(e-flipped) & $1.2439$ & $1.8500$ & $\mathbf{4.7073}$ \\ % 2_3
%(f) & $\mathbf{4.8292}$ & $2.0976$ & $1.2750$ \\ % 2_4
%(f-flipped) & $1.1463$ & $2.3171$ & $\mathbf{4.6585}$ \\ % 2_5
%\\
%\hline
%Domain & \multicolumn{3}{c}{Military Engagement/Safe Region} \\
%% ~ & \multicolumn{3}{c}{Average Likert Rating} \\
%Stim ID & P1 & P2 & P3\\
%(i) & $1.1951$ & $4.3902$ & $\mathbf{4.9024}$ \\ % 3_1
%(j) & $1.0952$ & $2.2927$ & $\mathbf{4.5122}$ \\ % 3_2
%(k) & $1.0714$ & $2.7804$ & $\mathbf{4.6585}$ \\ % 3_3
%(l) & $1.2327$ & $3.1667$ & $\mathbf{4.7073}$\\ % 3_4
%\\
%\hline
%\end{tabular}
%}
%\label{tab:point-likert-scores}
%\caption{Average Likert Ratings per Point by Domain and stimulus.}
%\end{table}
